A brief study of Approximation Algorithms for 2D Packing Problem

### 2021-12-10 paper.tex
proofread sec2

We already show that 2D Packing Problem is NP-Complete, and P vs NP remains an open problem, for which we probably cannot find an efficient algorithm to solve it deterministically. We must try another approach. To solve an inherently difficult problem, various approaches have been well-studied. For decision problems, we can use randomized algorithms to give the correct result with high probability. For optimization problems, we can use another approach: Approximation algorithm\cite{garey1976approximation} which is guaranteed to produce a sub-optimal but reasonable result. \par
In this paper, we are going to investigate various approximation algorithms for the 2D Packing Algorithm. In section 2, we will briefly study the definition and performance metric for Approximation algorithms. In section 3, we will introduce two early level-oriented heuristic approximation algorithms\cite{coffman1980performance} for 2D Packing Problem. In section 4,  we will study a more advanced approach\cite{steinberg1997strip}.

@@

For inherently difficult problems like NP-Complete problems, various approaches have been well-studied to efficiently solve them. The most common approach to solve an optimization problem is Approximation algorithms. Approximation algorithms aim to find an approximate solution to the optimal solution, then we can efficiently solve the target problem with a tight performance bound using approximation algorithm.\par
The analysis for Approximation algorithms often requires a thorough mathematical proof for the worst-case performance. We can find some surprising properties for hard problems through Approximation algorithms. Although all NP-Complete problems are equivalently difficult, their complexity varies from the perspective of Approximation algorithms. For example, there exist an algorithm for the Knapsack problem that can produce solutions that are arbitrarily close to the optimal result. However, finding a solution that is constant-bounded to the optimal result for the Maximum clique problem is proved to be equivalent to prove whether P = NP. Therefore, Approximation algorithms offer an extra, more fine-grained classification for NP-hard problems.\par
Now we are going to look at the performance metrics for Approximation algorithms.

@@

To measure the performance of approximation, we need to quantify the difference between the produced result and the optimal solution. The most commonly used metric is the multiplicative factor between the solution and the optimum. For problem $L$, assume that the algorithm is $A$, the optimal result is $OPT(L)$, the produced solution is $A(L)$:

@@

Then for minimization problems, Approximation ratio $\alpha$ puts a multiplicative maximum bound on the result $A(L) \leq \alpha*OPT(L)$. For maximization problems, approximation ratio puts a multiplicative minimum bound on the result $A(L) \geq \frac{OPT(L)}{\alpha}$. We can also call this ratio Absolute Approximation Ratios to be precise.

@@

Different from Absolute Approximation ratio that only uses a multiplicative bound factor, Asymptotic Approximation uses an additional additive bound factor. This gives us a more fine-grained metric to measure the performance of Approximation algorithms. For minimization problems, an Asymptotic bound $\alpha$ means that:

@@

$\gamma$ is an additive constant factor. It should be noticed that any asymptotic approximation ratio can be relaxed into a weaker absolute approximation bound.\par
After we introduce different metrics for measuring the performance of approximation algorithms, we will show how to analyze approximation algorithms using these metrics in the next section with 2 intuitive algorithms for 2D Packing.

>>>>

We already show that 2D Packing Problem is NP-Complete, and P vs NP remains an open problem, for which we probably cannot find an efficient algorithm to solve it deterministically. We must try another approach. To solve an inherently difficult problem, various approaches have been well-studied. For decision problems, we can use randomized algorithms to give the correct result with high probability. For optimization problems, we can use another approach: approximation algorithms\cite{garey1976approximation} which could produce a sub-optimal but reasonable result. \par
In this paper, we investigate various approximation algorithms for 2D Packing. In section 2, we briefly study the definition and performance metric for approximation algorithms. In section 3, we introduce two early level-oriented heuristic approximation algorithms\cite{coffman1980performance}. In section 4, we analyze a more advanced approach\cite{steinberg1997strip} which gives a tighter approximation bound. A brief conclusion and future investigation problems are given in section 5.

@@

For inherently difficult problems like NP-Complete problems, various approaches have been well-studied to efficiently solve them. The most common approach to solve an optimization problem is by utilizing approximation algorithms. Approximation algorithms aim to find an approximate solution to the optimal solution, with which we can solve the target problem efficiently with a tight performance bound.\par
The analysis for approximation algorithms often requires a thorough mathematical proof for the worst-case performance. We can find some surprising properties for hard problems through approximation. Although all NP-Complete problems are equivalently difficult, their complexity varies from the perspective of approximation algorithms. For example, there exist an algorithm for the Knapsack problem that can produce solutions that are arbitrarily close to the optimal result in polynomial time with respect to input size and precision. However, finding a solution that is constant-bounded to the optimal result for the Maximum clique problem is proved to be equivalent to prove whether P = NP. Therefore, approximation algorithms offer an extra, more fine-grained classification for NP-hard problems.

@@

To measure the performance of approximation, we need to quantify the difference between the produced result and the optimal solution. The most commonly used metric is the multiplicative factor between the solution and the optimum. For problem $L$, assume that the algorithm is $A$, the optimal result is $OPT(L)$, and the produced solution is $A(L)$:

@@

Then for minimization problems, approximation ratio $\alpha$ puts a multiplicative maximum bound on the result $A(L) \leq \alpha*OPT(L)$. For maximization problems, approximation ratio puts a multiplicative minimum bound on the result $A(L) \geq \frac{OPT(L)}{\alpha}$. We can also call this ratio Absolute Approximation Ratios to be precise.

@@

Different from Absolute Approximation ratio that only uses a multiplicative bound factor, Asymptotic Approximation uses an additional additive bound factor. This gives us a more fine-grained metric to measure the performance of Approximation algorithms. For minimization problems, the Asymptotic bound is $\alpha$ when

@@

where $\gamma$ is an additive constant factor. It should be noticed that any asymptotic approximation ratio can be relaxed into a weaker absolute approximation bound.\par
Now that we have introduced the metrics for measuring performance of approximation algorithms, we will apply these skills on analyzing 2 intuitive approximation algorithms for 2D Packing in the next section.
